---
title: "Quarto Example"
author: "Your Name"
date: "2023-10-05"
format: html
---

## Introduction

This is a short example demonstrating the setup and use of Quarto with both R 
and Python.

## Setup

First, ensure you have Quarto installed. You can download it from [quarto.org](https://quarto.org). 
I like working in Microsoft VSCode, so I found [this page](https://quarto.org/docs/tools/vscode.html) 
for VSCode's Quarto extension helpful to get started.

## Using R

Below is an example of an R code chunk:

```{r}
x <- rnorm(1000)
library(ggplot2)

# Create a data frame
data <- data.frame(x = x)

# Plot with ggplot2
ggplot(data, aes(x = x)) +
    geom_histogram(binwidth = 0.2, fill = "blue", color = "black") +
    labs(title = "Histogram of Gaussian Noise",
             x = "Value",
             y = "Frequency")
```

## Using Python

To use Python in your project, it is advisable to create a virtual environment. 
[This page](https://quarto.org/docs/projects/virtual-environments.html) gives 
some tips on creating and using a virtual environment and activating it for 
Quarto in VSCode, for example. I used Conda to make my environment (called 
`env`) in the same working directory as this Git repository. Then I created a 
file in the same directory called `.Rprofile` with this command:
```
Sys.setenv(RETICULATE_PYTHON = "env/bin/python")
```
I've also used VSCode's command palette to select my new environment as my 
Python interpreter, although I am not sure that this was required to knit my 
`.qmd`. Below is an example of a Python code chunk that is interpreted using 
some of the packages that I've installed in my conda environment:

```{r}
library(reticulate)
```

```{python}
import numpy as np
import matplotlib.pyplot as plt

# Generate Gaussian noise
noise = np.random.normal(0, 1, 1000)

# Plot the noise
plt.hist(noise, bins=30, edgecolor='k')
plt.title('Histogram of Gaussian Noise')
plt.xlabel('Value')
plt.ylabel('Frequency')
plt.show()
```